Modelling RNA-based oscillatory circuits

### 2015-09-26 Presentation/MscPresentation.tex
further presentation work

\usepackage{epstopdf,chemfig}
\usepackage{xcolor}
\DeclareMathOperator*{\argmin}{arg\,min}
\newenvironment{greyedout}{\color{gray}}{\ignorespacesafterend}

@@

\subsection{ODE Model for system}
\begin{frame}{ODE Model for system (1) - Complex Formation}{}
\begin{columns}
\column{.45\textwidth}
\includegraphics[trim = 135 0 0 0,clip = true,scale = 0.31]{Figures/schematic_binding}
\column{.5\textwidth}
  \begin{itemize}
    \item  Hybridization of sRNA \textcolor{blue}{($s$)} and mRNA \textcolor{blue}{($m$)}, into unstable complex \textcolor{blue}{($s:m$)} then stable one \textcolor{blue}{($c$)}.
    \end{itemize}
\footnotesize
\begin{align*} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\mu + \delta_{s})s -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\mu + \delta_{m})m -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m  \\
\frac{ds:m}{dt} & = k_{\mathrm{on}}sm  - (k_{\mathrm{off}}+ k_{\mathrm{hyb}})s:m  -(\mu + \delta_{sm} )s:m \\
\frac{dc}{dt} & = k_{\mathrm{hyb}}s:m  -(\mu + \delta_{c})c  \\
\end{align*}
\end{columns}
\end{frame}

\begin{frame}{ODE Model for system (2) - Translation}{}
\begin{columns}
\column{.45\textwidth}
\includegraphics[trim = 0 0 0 0,clip = true,scale = 0.31]{Figures/schematic_translation}
\column{.5\textwidth}
  \begin{itemize}
    \item Translation of stable complex \textcolor{blue}{($c$)} into immature GFP \textcolor{blue}{($p$)}. 
    \item maturation of GFP \textcolor{blue}{($g$)}, machine calibration giving measured fluorescence ($z$).
    \end{itemize}
\footnotesize
\begin{align*} 
\frac{dp}{dt} & = \beta m +f_{s}\beta c -(\gamma + \mu + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\mu + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\Theta} 
\end{align*}
\end{columns}
\end{frame}

@@

\small
\begin{frame}{Full model, with Parameters to be estimated}
\begin{align} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\alert{\mu} + \alert{\delta_{s}})s -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\alert{\mu} + \alert{\delta_{m}})m -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m  \\
\frac{ds:m}{dt} & = \alert{k_{\mathrm{on}}}sm  - (\alert{k_{\mathrm{off}}}+ \alert{k_{\mathrm{hyb}}})s:m  -(\alert{\mu} + \alert{\delta_{m}} )s:m \\
\frac{dc}{dt} & = \alert{k_{\mathrm{hyb}}}s:m  -(\alert{\mu} + \alert{\delta_{m}})c  \\
\frac{dp}{dt} & = \alert{\beta} m +\alert{f_{s}}\beta c -(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align}
\end{frame}
\normalsize

@@

\begin{frame}{Initial Estimation Results}
  \includegraphics[scale = 0.25, clip = true, trim = 0 0 0 0]{Figures/13_9_hist}
        \begin{itemize}
    \item Many parameters poorly estimated.
            \end{itemize}
\end{frame}

\begin{frame}{Sensitivity Analysis}
  \includegraphics[scale = 0.2, clip = true, trim = 00 0 0 0]{Figures/Sensitivty_scaled_other}
  \vspace{-2mm}
          \begin{itemize}
    \item Sensitivity analysis suggests perturbations of several parameters all give similar effects on model output - \alert{hard to resolve}
            \end{itemize}
\end{frame}

\begin{frame}{Model output for all state variables}
  \includegraphics[scale = 0.25, clip = true, trim = 30 0 0 0]{Figures/model_output}
\end{frame}

@@

\begin{frame}{Simplified Model Results (1)}
  \includegraphics[scale = 0.28, clip = true, trim = 100 0 0 400]{../Figures/13_9_hist_simplified}
  \begin{itemize}
\item  Error values as low as full model
\item Clearer parameter estimation results
\item Two peak structure due to local minima
\end{itemize}
\end{frame}

\begin{frame}{Simplified Model Results (2)}
  \includegraphics[scale = 0.25, clip = true, trim = 0 0 0 0]{Figures/Likelihood_rough_presentation}
    \begin{itemize}
\item  Error landscape, $\Theta = 5400$.
\end{itemize}
\end{frame}

>>>>

\usepackage{epstopdf,chemfig}
\usepackage{xcolor}
\DeclareMathOperator*{\argmin}{arg\,min}
\newenvironment{greyedout}{\color{gray}}{\ignorespacesafterend}
\setbeamercolor{alerted text}{fg = red}

@@

\subsection{ODE Model for system}
\begin{frame}{ODE Model for system (1) - Complex Formation}{}
\begin{columns}
\column{.4\textwidth}
\includegraphics[trim = 135 0 0 0,clip = true,scale = 0.28]{Figures/schematic_binding}
\column{.6\textwidth}
  \begin{itemize}
    \item  Hybridization of sRNA \textcolor{blue}{($s$)} and mRNA \textcolor{blue}{($m$)}, into unstable complex \textcolor{blue}{($s:m$)} then stable one \textcolor{blue}{($c$)}.
    \end{itemize}
\footnotesize
\begin{align*} 
\frac{d\textcolor{blue}{s}}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\mu + \delta_{s})s -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m \\
\frac{d\textcolor{blue}{m}}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\mu + \delta_{m})m -k_{\mathrm{on}}sm +k_{\mathrm{off}}s:m  \\
\frac{d\textcolor{blue}{s:m}}{dt} & = k_{\mathrm{on}}sm  - (k_{\mathrm{off}}+ k_{\mathrm{hyb}})s:m  -(\mu + \delta_{sm} )s:m \\
\frac{d\textcolor{blue}{c}}{dt} & = k_{\mathrm{hyb}}s:m  -(\mu + \delta_{c})c  \\
\end{align*}
\end{columns}
\end{frame}

\begin{frame}{ODE Model for system (2) - Translation}{}
\begin{columns}
\column{.4\textwidth}
\includegraphics[trim = 0 0 0 0,clip = true,scale = 0.31]{Figures/schematic_translation}
\column{.6\textwidth}
  \begin{itemize}
    \item Translation of stable complex \textcolor{blue}{($c$)} into immature GFP \textcolor{blue}{($p$)}. 
    \item maturation of GFP \textcolor{blue}{($g$)}, machine calibration giving measured fluorescence ($z$).
    \end{itemize}
\footnotesize
\begin{align*} 
\frac{d\textcolor{blue}{p}}{dt} & = \beta m +f_{s}\beta c -(\gamma + \mu + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{d\textcolor{blue}{g}}{dt} & = \gamma p - (\mu + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\Theta} 
\end{align*}
\end{columns}
\end{frame}

@@

\small
\begin{frame}{Full model, with Parameters to be estimated}
\begin{align} 
\frac{ds}{dt} &= \frac{N\alpha_{T}}{f_{T}} y(t)-(\alert{\mu} + \alert{\delta_{s}})s -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m \\
\frac{dm}{dt} &=  \frac{N\alpha_{L}}{f_{L}}x(t)-(\alert{\mu} + \alert{\delta_{m}})m -\alert{k_{\mathrm{on}}}sm +\alert{k_{\mathrm{off}}}s:m  \\
\frac{ds:m}{dt} & = \alert{k_{\mathrm{on}}}sm  - (\alert{k_{\mathrm{off}}}+ \alert{k_{\mathrm{hyb}}})s:m  -(\alert{\mu} + \alert{\delta_{m}} )s:m \\
\frac{dc}{dt} & = \alert{k_{\mathrm{hyb}}}s:m  -(\alert{\mu} + \alert{\delta_{m}})c  
\end{align}
\begin{center}
\rule{0.5\textwidth}{.4pt}
\end{center}
\begin{align}
\frac{dp}{dt} & = \alert{\beta} m +\alert{f_{s}}\beta c -(\gamma + \alert{\mu} + \delta_{g})p - \frac{v_{z}p}{K_{z}+p+g}   \\
\frac{dg}{dt} & = \gamma p - (\alert{\mu} + \delta_{g})g - \frac{v_{z}g}{K_{z}+p+g} \\
z &= z_{0} +\frac{g}{\alert{\Theta}} 
\end{align}
\end{frame}
\normalsize

@@

\begin{frame}{Initial Estimation Results}
  \includegraphics[scale = 0.28, clip = true, trim = 130 0 0 0]{Figures/13_9_hist}
        \begin{itemize}
    \item Many parameters poorly estimated.
            \end{itemize}
\end{frame}

\begin{frame}{Sensitivity Analysis}
  \includegraphics[scale = 0.25, clip = true, trim = 00 0 0 0]{Figures/Sensitivty_scaled_other}
  \vspace{-2mm}
          \begin{itemize}
    \item Sensitivity analysis suggests perturbations of several parameters all give similar effects on model output - \alert{hard to resolve}
            \end{itemize}
\end{frame}

\begin{frame}{Model output for all state variables}
  \includegraphics[scale = 0.29, clip = true, trim = 0 0 0 0]{Figures/model_output}
\end{frame}

@@

\begin{frame}{Simplified Model Results (1)}
  \includegraphics[scale = 0.29, clip = true, trim = 100 0 0 400]{Figures/13_9_hist_simplified}
  \begin{itemize}
\item  Error values as low as full model
\item Clearer parameter estimation results
\item Two peak structure due to local minima
\end{itemize}
\end{frame}

\begin{frame}{Simplified Model Results (2)}
  \includegraphics[scale = 0.26, clip = true, trim = 40 0 0 0]{Figures/Likelihood_rough_presentation}
    \begin{itemize}
\item  Error landscape, $\Theta = 5400$.
\end{itemize}
\end{frame}
